% LaTeX file for resume 

\documentclass[11pt]{article} 

\usepackage[left=3.0cm, right=2.50cm, top=3.00cm, bottom=3.00cm]{geometry}%page margin

\usepackage{titlesec}%for section settings
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}%space after and before section

\setlength\parindent{0pt}%no indent
\usepackage{fancyhdr} %for header/footer

\pagestyle{fancy}%for footer
\fancyhf{}
\lfoot{Curriculum Vitae - Tuyen Le}%footer
\rfoot{Page \thepage\ of 4} %page no
\renewcommand{\headrulewidth}{0in}%remove underline in header

%\usepackage{pslatex} %Times font
\usepackage[T1]{fontenc}
\usepackage{fbb}

\usepackage{enumitem}
%\setlist{noitemsep}%alternative way
\setlist{nosep,topsep=0pt,after=\vspace{\baselineskip}}%no space before and within list, with space after list

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
{\huge\bf Tuyen T. Le,} {\large\bf Ph.D. Candidate}\\ % Your name at the top
\noindent\rule{\linewidth}{1.25pt}
Department of Civil, Construction and Environmental Engineering\\ % Your address
Iowa State University, Ames, Iowa 50014\\
Phone: (515) 203-5273; Email: ttle@iastate.edu
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section*{EDUCATION}

{\sl Ph.D., Civil Engineering}  \hfill August 2014 - May 2017 (expected) \\
Iowa State University, Ames, Iowa\\
Advisor: Dr. H. David Jeong\\
Dissertation: ``Natural Language based Partial Model Extraction from Linked Life-Cycle Infrastructure Data Space"\\

{\sl M.S., Construction Engineering and Management}  \hfill August 2012 - December 2013 \\
Ho Chi Minh City University of Technology, Ho Chi Minh, Vietnam\\
Advisor: Dr. Long Duc Luong\\
Thesis: ``Developing a 4D-BIM based Scheduling Framework for Repetitive Projects"\\

{\sl B.E. with Honors, Civil Engineering}  \hfill August 2006 - December 2010 \\
Ho Chi Minh City, University of Technology, Ho Chi Minh, Vietnam
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section*{RESEARCH EXPERIENCE}

{\sl Graduate Research Assistant} \hfill August 2014 - present \\
Iowa State University, Ames, Iowa
\begin{itemize}
\item Lead researcher of project: ``Guide to Data and Information Sharing Workflows across the Life Cycle of Transportation Assets". Conducted interviews with DOT staff and documented the current practices of life-cycle data sharing.
\item Lead researcher of NSF project: ``Natural Language Based Data Retrieval Engine for Automated Digital Data Extraction for Civil Infrastructure Projects". Developed a classifier to detect term inconsistency and constructed a digital dictionary of highway technical terms.
\item Developed a computational platform for interlinking data generated during the life-cycle of an infrastructure project.
\end{itemize}

{\sl Graduate Research Assistant} \hfill December 2013 - May 2014 \\
Singapore National University, Singapore
\begin{itemize}
\item Designed an algorithm for finding the optimal layout of room functions in hospital projects.
\end{itemize}

{\sl Lecturer} \hfill September 2011 - December 2013 \\
Ho Chi Minh City University of Technology
\begin{itemize}
\item Developed a computerized model for scheduling non-repetitive and repetitive projects under correlated uncertainties.
\item Implemented 4D-BIM in scheduling and controlling the construction process of repetitive projects.
\end{itemize} 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section*{TEACHING and MENTORING EXPERIENCE}

{\sl Research Mentor} \hfill August 2016 - present \\
Iowa State University, Ames, Iowa
\begin{itemize}
\item Supervised a senior student (Alan Hayes) on a funded project. 
\item Provided him with guidance on data collection and analysis, and edited his writing reports.
\end{itemize} 

{\sl Instructor} \hfill August 2015 - present \\
Iowa State University, Ames, Iowa
\begin{itemize}
\item Course: CE594A - Planning and Scheduling (Spring 2015, Fall 2015, Spring 2016, Fall 2016)
\item Updated syllabus, assignments and exams. Managed the class and responded to questions.
\end{itemize}

{\sl Guest Lecturer} \hfill October 2016 \\
Iowa State University, Ames, Iowa
\begin{itemize}
\item Course: CE595A - Research Method in Construction Engineering and Management (Fall 2016) 
\item Developed and delivered a lecture on the implementation of NLP in civil engineering.
\end{itemize}

{\sl Lecturer} \hfill September 2011 - December 2013 \\
Ho Chi Minh City University of Technology
\begin{itemize}
\item Courses: 807012 - Economics in Construction; 807018 - Construction Project Management.
\item Designed and delivered lectures. 
\end{itemize} 
%----------------------------------------------------------------------------------------
%	GRANTS
%----------------------------------------------------------------------------------------
\section*{GRANTs}

{\sl National Science Foundation (NSF)} \hfill September 2016 - September 2019 
\begin{itemize}
\item Project title: ``Natural Language Based Data Retrieval Engine for Automated Digital Data Extraction for Civil Infrastructure Projects" ({\bf Total Awarded}: \$285,305)
\item Role: Lead proposal contributor (PI: David Jeong)
\end{itemize} 

{\sl Iowa Highway Research Board (IHRB) and Midwest Transportation Center (MTC)} \hfill August 2016 - January 2018
\begin{itemize}
\item Project title: ``Guide to Data and Information Sharing Workflows across the Life Cycle of Transportation Assets" ({\bf Total Awarded:} \$180,000)
\item Role: Lead proposal contributor (PI: David Jeong)
\end{itemize} 

{\sl Project Management Institute (PMI)} \hfill December 2016 - October 2017
\begin{itemize}
\item Project title: ``Cutting-Edge Advancements in Project Management from across Industry Sectors" (pending)
\item Role: Lead proposal contributor (PI: David Jeong)
\end{itemize}

{\sl Project Management Institute (PMI)} \hfill January 2016 -  December 2017
\begin{itemize}
\item Project title: ``Project Analytics: Integrating Project Management with Big Data" (unsuccessful)
\item Role: Lead proposal contributor (PI: David Jeong)
\end{itemize}

{\sl Midwest Transportation Center (MTC)} \hfill January 2015 - July 2017
\begin{itemize} 
\item Project title: ``Guide to Transferring Design and Construction Data to Asset Management" (unsuccessful)
\item Role: Major proposal contributor (PI: David Jeong)
\end{itemize}

{\sl Ho Chi Minh City University of Technology } \hfill May 2013 - May 2014
\begin{itemize}
\item Project title: ``A 4D-based scheduling framework for repetitive projects" ({\bf Total Awarded}: \$1,000)
\item Role: Principle Investigator (Co-PI: Long Duc Luong)
\end{itemize}
%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%---------------------------------------------------------------------------------------- 
\section*{PUBLICATIONs}

\subsection*{\sl Peer-Reviewed Journal Articles}
{\bf Le, T.} and Jeong, H. D. (2016). ``NLP-based approach to classifying heterogeneous terms for unambiguous exchange of highway data." Journal of Computing in Civil Engineering, ASCE. (In second review)\\
{\bf Le, T.} and Jeong, H. D. (2016). ``Interlinking life-cycle data spaces to support decision making in highway asset management." Automation in construction 64: 54-64.

\subsection*{\sl Manuscripts in Preparation (for submission within the academic year)}
{\bf Le, T.} and Jeong, H. D. (in preparation). ``Automated extraction for partial BIM model using context-aware searching algorithm." Journal of Computing in Civil Engineering, ASCE.\\
{\bf Le, T.} and Jeong, H. D. (in preparation). ``An extensive civil engineering lexicon." Automation in Construction.

\subsection*{\sl Peer-Reviewed Conference Papers  (presenter underlined)}
{\bf \underline{Le, T.}} and Jeong, H. D. (2016). Technical term similarity model for natural language based data retrieval in civil infrastructure projects. Proceedings of 33rd International Symposium on Automation and Robotics in Construction (ISARC 2016), Jul 2016, Auburn, Alabama, USA\\
{\bf \underline{Le, T.}} and Jeong, H. D. (2016). A framework for inter-connection of life-cycle highway data islands. Proceedings of 2016 Construction Research Congress (CRC2016), June 2016, Puerto Rico, USA.\\
{\bf \underline{Le, T.}} and Luong, D.L., (2013). Scheduling method for repetitive projects under correlated uncertainties. In 13th Conference on Science and Technology - Structure \& Architecture Session-2013 HCMUT Vietnam- Faculty of Civil Engineering. pp. 1?8. Ho Chi Minh City, Vietnam.

\subsection*{\sl Presentations with abstract reviewed (presenter underlined)} 
{\bf Le, T.} and  \underline{Jeong, H. D.}  (2016). Measuring synonymy of data attributes from heterogeneous sources in transportation projects, US-Korea Conference, August 2016, Dallas, Texas, USA.\\
{\bf \underline{Le, T.}}  and Jeong, H. D. (2015). Data extraction from highway information model. 2015 Mid-Continent Transportation Research Symposium. Ames, United States. \\
{\bf \underline{Le, T.}}  and Jeong, H. D. (2015). A digital dictionary of highway technical terms. 5th Annual CCEE Graduate Student Research Showcase and Poster Competition. Ames, United States.

\subsection*{\sl Non Peer-Reviewed Articles}
{\bf Le, T.} and Luong, D.L., (2013). ``Developing a 4D-BIM model for scheduling repetitive projects." Vietnamese Journal of Construction, 12-2013, pp.100-103.\\
{\bf Le, T.} and Luong, D.L., (2013). ``Scheduling under correlated uncertainties." Vietnamese Journal of Construction, 08-2013, pp.66-71.
%----------------------------------------------------------------------------------------
%	HORNORS
%---------------------------------------------------------------------------------------- 
\section*{HORNORs and AWARDs}
Iowa State University Graduate Assistantship \hfill 2015 - present\\
Travel grant from GPSS, Iowa State University (\$180) \hfill January 2016\\
Travel grant from CCEE Department, Iowa State University (\$350) \hfill May 2016\\
Iowa State University Presidential Scholars (\$30,000) \hfill 2014 - 2015\\
Outstanding Young Staff Award, Ho Chi Minh City University of Technology \hfill 2013\\
Gold Medal for the best bachelor's degree graduate, Ho Chi Minh City University of Technology \hfill 2011\\
Loa Thanh Award (ranked 2nd) for excellent undergraduate theses, Vietnam Ministry of Education and Training \hfill 2011\\
Bronze Medal in the Vietnam National Mechanics Olympiad, Vietnam Ministry of Education and Training \hfill 2009\\
Kiatagawa scholarship (\$500) \hfill 2009 \& 2011\\
Lawrence Sting scholarship \& Pony Chung scholarship (Total \$1,000) \hfill 2008\\
Viet-Japan scholarship (\$100) \hfill 2007\\
Investlife scholarship \& Viethope scholarship (Total \$200) \hfill 2006
%----------------------------------------------------------------------------------------
%	PROFESSIONAL SERVICES
%---------------------------------------------------------------------------------------- 
\section*{PROFESSIONAL SERVICEs}
{\sl Journal reviewer} \hfill 2015 - present\\
Journal of Construction Engineering and Management - ASCE (02 manuscripts)\\
Construction Research Congress - ASCE (01 manuscript)\\
Transportation Research Board - Annual Meetings (02 manuscripts)

\section*{PROFESSIONAL AFFILIATIONs}
American Society of Civil Engineers (ASCE), Member (2015-present)
 

%----------------------------------------------------------------------------------------

%\end{resume}
\end{document}